Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-31 paper/src/paper.tex
lambda value 0

@@

Readers interested in replicating the experiments (or a part thereof) are
invited to peruse to the 'artifacts description' appendix of this paper.  We
provide to persistent archives containing the simulator, the analysis code and
an automated workflow that replicates all experiments and figures present in
this paper.

>>>>

We use devise the following experimental campaign. For each workload trace
considered, we use the original data to resample 100 traces, each of a length
of two years. For each resampled trace, we run simulations using the
EASY($P,\Theta$) scheduling heuristic. We fix the value of the job waiting time
threshold $\Theta$ at 40 hours, a sane default. The choice of this default
stems from the analysis developped in ~\cite{jsspp17}. This value is high
enough for queue reorderings to be leveraged while being low enough to provide
the functional requirement of preventing starvation. We simulate
EASY($P,\Theta=40h$) using the following policies:

\begin{itemize}
  \item All fixed $P_i$ for $1<i<10$.
  \item The simulation-based ("full feedback") strategy.
  \item The noisy simulation ("noisy feedback") variant.
  \item The bandit feedback strategy with a fixed value of $\lambda=0$.
\end{itemize}

This campaign of 7 (traces) * 100 (resampling) * 13 Policies

@@

Readers interested in replicating the experiments (or a part thereof) are
invited to peruse the 'artifacts description' appendix of this paper. We
provide to persistent archives containing the simulator, the analysis code and
an automated workflow that replicates all experiments and figures present in
this paper with automatic dependency management.
